### 2020-11-13 docs/manuscript/PLOS-MSc-Thesis.tex
citate santos-moreno&schaerli 2019
add author summary and reformat affiliations

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory 
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1\Yinyang},
Gloria Machado-Rodríguez\textsuperscript{1\Yinyang},
Boris Rodríguez-Rey\textsuperscript{2\textcurrency},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Instituto de Biología, Universidad de Antioquia, Medellín,
Antioquia, Colombia
\\
\textbf{2} Instituto de Física, Universidad de Antioquia, Medellín, Antioquia,
Colombia
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Curabitur eget porta 
erat. Morbi consectetur est vel gravida pretium. Suspendisse ut dui eu ante 
cursus gravida non sed sem. Nullam sapien tellus, commodo id velit id, eleifend 
volutpat quam. Phasellus mauris velit, dapibus finibus elementum vel, pulvinar 
non tellus. Nunc pellentesque pretium diam, quis maximus dolor faucibus id. Nunc
convallis sodales ante, ut ullamcorper est egestas vitae. Nam sit amet enim 
ultrices, ultrices elit pulvinar, volutpat risus.

@@

Our understanding of how GRNs process information has increased thanks to the
concept and theory of network motifs, which are defined as patterns of
interconnections occurring in networks at numbers that are significantly higher
than those in randomized networks \cite{Milo2002}. This novel approach, along
with mathematical modeling and computational methods have been shown to be a
powerful tool to study GRNs and the predictions of studies using these methods
have been validated by experimental studies
\cite{Kalir2005,Kalir2004,Mangan2003a,ODonnell2005}, and some of them 
have even used synthetic GRNs to produce artificial cell differentiation~\cite{Basu2005} 
and circadian gene expression~\cite{atkinson_development_2003}.

>>>>

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Elucidating multi-input processing 3-node gene regulatory 
network topologies capable of generating striped gene expression patterns}
% Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Juan Camilo Arboleda-Rivera\textsuperscript{1\Yinyang},
Gloria Machado-Rodríguez\textsuperscript{1\Yinyang},
Boris Rodríguez-Rey\textsuperscript{2\textcurrency},
Jayson Gutiérrez\textsuperscript{3},
% Name5 Surname\textsuperscript{2\ddag},
% Name6 Surname\textsuperscript{2\ddag},
% Name7 Surname\textsuperscript{1,2,3*},
% with the Lorem Ipsum Consortium\textsuperscript{\textpilcrow}
\\
\bigskip
\textbf{1} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Biología, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{2} Grupo de Fundamentos y Enseñanza de la Física y los Sistemas Dinámicos,
Instituto de Física, Facultad de Ciencias Exactas y Naturales, Universidad de Antioquia
UdeA, Calle 70 No. 52-21, Medellín, Colombia.
\\
\textbf{3} Flanders Marine Institute (VLIZ), Wandelaarkaai 7, 8400 Oostende,
Belgium
% \textbf{3} Affiliation Dept/Program/Center, Institution Name, City, State, Country
\\
\bigskip

@@

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}
Systems biology is growing very quickly thanks to the advances in computing and
mathematical modeling of biological systems, and has proven to be a powerful tool that
can help us to understand complex biological processes such as pattern formation and
development. In this article we use an \textit{in silico} approach in order to find and study
the design space of three node Gene Regulatory Networks that are able to produce a 
striped pattern of gene expression.

@@

Our understanding of how GRNs process information has increased thanks to the
concept and theory of network motifs, which are defined as patterns of
interconnections occurring in networks at numbers that are significantly higher
than those in randomized networks \cite{Milo2002}. This novel approach, along
with mathematical modeling and computational methods have been shown to be a
powerful tool to study GRNs and the predictions of studies using these methods
have been validated by experimental studies
\cite{Kalir2005,Kalir2004,Mangan2003a,ODonnell2005}, and some of them 
have even used synthetic GRNs to produce artificial cell differentiation~\cite{Basu2005} 
and circadian gene expression~\cite{atkinson_development_2003}. Moreover, 
the design and implementation of GRNs through synthetic biology is emerging as 
a promising tool to study biological phenomena as pattern formation 
\cite{santos-moreno_using_2019}.
